---
  title: "Testes"
author: "Christopher Eshleman"
date: "5/12/2018"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

There's data out there on business generation. 

A count of new businesses could be used, for example, as an indicator of general business conditions, particularly if the parent analysis included the right controls. 

A quick peeek at the univariate distribution will offer clues. 

The data comes from the City of New York Department of Consumer Affairs. It's a tally, by year, of the firms or people securing and holding a City license so that they may "legally operate in New York City". It excludes, for whatever reason, sightseeing guides and temporary street fair vendors, but that can't be a big number we I'll call it the population of City license-holders. 

```{r business, echo=FALSE}
cat("\014") 
rm(list=ls())
dev.off() 

library(plyr) 
library(doBy) 
library(rgdal) 
library(ggplot2) 
library(zipcode) 
```

I'm not sure I'll need all these packages yet but, eventually, I'll be mapping this stuff. Load the data, extract the year and count annual observations by ZIP code. 

```{r, echo=FALSE}
biz = read.csv("/Users/chriseshleman/Dropbox/Research_and_training_2/Business/Legally_Operating_Businesses.csv") 
biz$year = format(as.Date(biz$License.Creation.Date, format="%d/%m/%Y"),"%Y")
today = subset(biz,biz$year==2016) 
today$one = 1 
tab = summaryBy(one ~ year + Address.ZIP, FUN=sum, data=today) 
```

There are more unique ZIP codes in here than there should be. I'll plow through that for now and figure it out on the flip side. 

Import the shapefiles by ZIP code. 

```{r, echo=FALSE, results="hide"}
temp = tempfile() 
url="https://data.cityofnewyork.us/download/i8iw-xf4u/application%2Fzip" 
download.file(url, temp) 
unzip(temp,exdir=getwd()) 
zips = readOGR("/Users/chriseshleman/Dropbox/Research_and_training_2/Business/ZIP_CODE_040114/ZIP_CODE_040114.shp","ZIP_CODE_040114") 

show = ggplot(data = tab) + 
  geom_boxplot(mapping = aes("var",one.sum)) + 
  xlab("") + 
  ylab("New businesses by ZIP code") + 
  scale_x_discrete(breaks=NULL) + 
  coord_flip()
ggsave(show,file="/Users/chriseshleman/Dropbox/Research_and_training_2/Business/Box by ZIP 20180512.png",units="cm",width=12,height=8) 
```
